Powdery mildew yield loss mitigation strategies in mungbean, a meta-analysis.

### 2020-02-22 01_Meta-analysis_experiments.Rmd
Update 01_Meta-analysis_experiments.Rmd
Use kable styling

```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}

PM.dat <- import_data()

kable(
   PM.dat %>%
      group_by(
         trial_ref,
         year,
         location,
         trial_design,
         replicates,
         planting_date,
         emergence_date,
         first_sign_disease
      ) %>%
      summarise(treatments = length(n_treatment)),
   caption = "Description of Experiments"
 ) # %>%  #commented as was redering empty, needs a look in
#    kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
#    scroll_box(width = "900px", height = "500px")

>>>>

```{r data_summary, echo=TRUE, message=FALSE, warning=FALSE}
PM.dat <- import_data()

kable(
   PM.dat %>%
      group_by(
         trial_ref,
         year,
         location,
         trial_design,
         replicates,
         planting_date,
         emergence_date,
         first_sign_disease
      ) %>%
      summarise(treatments = length(n_treatment)),
   caption = "Description of Experiments"
)  %>%
   kable_styling(fixed_thead = TRUE, full_width = TRUE) %>%
   scroll_box(width = "900px", height = "500px")
